\Title

### 2023-03-01 Grimaldi-etal-BiolCybernetics.tex
Update on Overleaf.

We observe some facts of interest. First, as we change the mean spatial frequency of the texture, we observe a monotonous decrease in accuracy. This comes as a similar trend as that observed in the primary visual areas~\citep{priebe_tuning_2006} and revels the most informative scales learned by our model. We observe the tendency for different spatial frequency bandwidth. Notably, the accuracy is better for a grating-like stimulation than for a large (which qualitatively resemble a more textured stimulus), reminiscent to the behavioral response of humans to such stimuli~\citep{simoncini_more_2012}. Interestingly, we also see a modulation of accuracy as a function of orientation bandwidth. When the stimulus is grating-like and that the orientation is arbitrary with respect to the direction of motion, the system is faced with the aperture problem and see a decrease of accuracy. This is not the case for isotropic stimuli or when the orientation is perpendicular to the direction of motion. Finally, we manipulated the amount of change between two successive frames, similar to a temperature parameter. This shows a progressive decrease in accuracy, similar to that observed in the amplitude of humans' eye movements~\citep{mansour_pour_speed_2018}. % but also that accuracy is low for a rigid motion which lacks variability.
%
\subsection{Accuracy efficiency trade-off}% for the motion detection task}
%%%-----------------------------------------------------------------
Once our MLR is trained, we obtain spatio-temporal kernels corresponding to the weights associated to the heterogeneous delays of our layer of spiking neurons and which may be used for detection. We observed that the distribution of the kernels' weights is sparse, with most values near zero (\seeFig{kernels}). As shown in the formalization of our event-based model, the computational cost of our model if implemented on a neuromorphic chip would be dominated by the computations used for the convolution operation. In a dense setting, this corresponds for all voxels in the output to a sum over all voxels in the inputs for all weights in the kernel. If the support of information is sparse, then computations can be performed only on those events. Also, if we set some weights of the kernels to zero, then the sum can be skipped for those addresses. Knowing the sparseness of the input, the total number of computations thus scales with the number of spikes multiplied by the number of nonzero synaptic weights. % , which is proportional to the number of spikes multiplied by the number of synapses

>>>>

We observe some facts of interest. First, as we change the mean spatial frequency of the texture, we observe a monotonous decrease in accuracy. This comes as a similar trend as that observed in the primary visual areas~\citep{priebe_tuning_2006} and revels the most informative scales learned by our model. We observe the tendency for different spatial frequency bandwidth. Notably, the accuracy is better for a grating-like stimulation than for a large (which qualitatively resemble a more textured stimulus), reminiscent to the behavioral response of humans to such stimuli~\citep{simoncini_more_2012, ravello_speed-selectivity_2019}. Interestingly, we also see a modulation of accuracy as a function of orientation bandwidth. When the stimulus is grating-like and that the orientation is arbitrary with respect to the direction of motion, the system is faced with the aperture problem and see a decrease of accuracy. This is not the case for isotropic stimuli or when the orientation is perpendicular to the direction of motion. Finally, we manipulated the amount of change between two successive frames, similar to a temperature parameter. This shows a progressive decrease in accuracy, similar to that observed in the amplitude of humans' eye movements~\citep{mansour_pour_speed_2018}. % but also that accuracy is low for a rigid motion which lacks variability.
%
\subsection{Accuracy efficiency trade-off}% for the motion detection task}
%%%-----------------------------------------------------------------
Once our MLR is trained, we obtain spatio-temporal kernels corresponding to the weights associated to the heterogeneous delays of our layer of spiking neurons and which may be used for detection. We observed that the distribution of the kernels' weights is sparse, with most values near zero (\seeFig{kernels}). As shown in the formalization of our event-based model, the computational cost of our model if implemented on a neuromorphic chip would be dominated by the computations used for the convolution operation. In a dense setting, this corresponds for all voxels in the output to a sum over all voxels in the inputs for all weights in the kernel. If the support of information is sparse, then computations can be performed only on those events. Also, if we set some weights of the kernels to zero, then the sum can be skipped for those addresses. Knowing the sparseness of the input, the total number of computations thus scales with the number of spikes multiplied by the number of nonzero synaptic weights. % , which is proportional to the number of spikes multiplied by the number of synapses
